Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-07-06 ms.tex
added text to explain the regions affected by telluric absorption

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity.
	Each wavelength bin is labeled on the right side. Changing colors are used to distinguished the light curves with offsets. \sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
	\label{fig:tserDetrend}
\end{figure*}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_tser_no_detrend.pdf}
	\label{fig:tserPhase0835NoDetrend}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_tser_no_detrend.pdf}
	\label{fig:tserPhase1821NoDetrend}
	}
	\caption{Time series for each system with an offset added for clarity, as in Fig \ref{fig:tserDetrend}, but in this case showing the raw light curves without de-trending.
	Each wavelength bin is labeled on the right side. Significant variations in the baseline are modeled as linear functions of airmass and time which are most prominent near telluric absorption features at 1.38$\mu$m and 1.87$\mu$m.}
	\label{fig:tserNoDetrend}
\end{figure*}

>>>>

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity.
	Each wavelength bin is labeled on the right side. Changing colors are used to distinguished the light curves with offsets. \sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.
	Green brackets show regions where telluric absorption can contaminate the time series.}
	\label{fig:tserDetrend}
\end{figure*}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_tser_no_detrend.pdf}
	\label{fig:tserPhase0835NoDetrend}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_tser_no_detrend.pdf}
	\label{fig:tserPhase1821NoDetrend}
	}
	\caption{Time series for each system with an offset added for clarity, as in Fig \ref{fig:tserDetrend}, but in this case showing the raw light curves without de-trending.
	Each wavelength bin is labeled on the right side. Significant variations in the baseline are modeled as linear functions of airmass and time which are most prominent near edges of telluric absorption features at 1.32$\mu$m and 1.81$\mu$m.
	Green brackets show regions where telluric absorption can contaminate the time series.}
	\label{fig:tserNoDetrend}
\end{figure*}
